A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers

### 2018-02-22 article.tex
按照杨老师的要求进行了细微的调整，包括表格的错误

To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
Results show that the AOC is an effective method to reduce the superheat degree and improve the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system adopting 10-stage extractions and two outer steam coolers. 
The result of thermodynamic and techno-economic analyses shows this system can reduce cost of electricity to 55.89 USD/MWh.
Besides, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine to utilize the superheat degree of the extractions.
In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine not the regenerative heater.
Extractions from the intermediate pressure turbine are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design, and the exergy destruction of regenerative heaters is reduced, which results in an overall improvement in efficiency.

>>>>

To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum,Zhou2014A} investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
Results show that the AOC is an effective method to reduce the superheat degree and improve the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system adopting 10-stage extractions and two outer steam coolers. 
The result of thermodynamic and techno-economic analyses shows this system can reduce cost of electricity to 55.89 USD/MWh.
Besides, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine to utilize the superheat degree of the extractions.
In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine not the regenerative heater.
Extractions from the intermediate pressure turbine are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design, and the exergy destruction of regenerative heaters is reduced, which results in an overall improvement in efficiency.
